Supporting information

### 2023-11-01 paper/main.tex
submitted version

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, enhanced, boxrule=0pt, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

>>>>

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, sharp corners, breakable, interior hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

### 2023-11-01 paper/supporting_information.tex
submitted version

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt, interior hidden, sharp corners, breakable, enhanced]}{\end{tcolorbox}}\fi

@@

\leavevmode\vadjust pre{\hypertarget{ref-popova_generalization_1975}{}}%
Popova, S V, and E E Sel'kov. 1975. {``Generalization of the Model by
{Monod}, {Wyman} and {Changeux} for the Case of a Reversible
Monosubtrate Reaction {SR},{TP}.''} \emph{FEBS Letters} 53 (3): 269--73.
\url{https://doi.org/10.1016/0014-5793(75)80034-2}.

>>>>

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

\leavevmode\vadjust pre{\hypertarget{ref-popova_generalization_1975}{}}%
Popova, S V, and E E Sel'kov. 1975. {``Generalization of the Model by
{Monod}, {Wyman} and {Changeux} for the Case of a Reversible
Monosubtrate Reaction {\(S\overleftrightarrow{(R,T)}P\)}.''} \emph{FEBS
Letters} 53 (3): 269--73.
\url{https://doi.org/10.1016/0014-5793(75)80034-2}.
